% ************************** Thesis Acknowledgements *****************************

\begin{acknowledgements}      
\noindent First of all, I must extend my thanks to my supervisor, Prof.\,Jeremy Baumberg. His enthusiasm and guidance have been much appreciated throughout my PhD, and I am grateful to have been a part of the NanoPhotonics Centre over the last 4 years.

I would also like to thank all our group members, past and present. The suggestions and advice that came from group meetings have been extremely useful in stimulating new ideas and providing insights. A special mention must go to Dr.\,Matthew Hawkeye for his invaluable help in the early part of my PhD. Thanks for taking the time to listen to my incoherent ramblings every week! I can't say I was sad to see the end of those 9\,am meetings though. A humongous thank you to Lindsey and Matt as well - the past 4 years would not have been the same without you. Thanks for all the good times, the sympathy during bad times, and all the delicious food. Friday afternoons will never be the same again, even though we never managed to get that helicopter.

The Nanophotonic research group at IIT Delhi have also provided a great deal of support to me. My work would not have been possible without the material fabricated by Shahab Ahmad and Nageswara Kotla. And I am extremely grateful to Dr.\,G.\,Vijaya Prakash for all of his wonderful help and advice. It's been an absolutely pleasure to get to know you all, and it's amazing how you always have the answers to my questions.

I am indebted to my thesis beta-readers: Lindsey, Nadine, Vijay and Jeremy. Thanks for making sense of my ramblings. Thanks also to Daniel, whose simulation results are included in Chapter 2. I'd like to thank Anna Eiden for showing me how much fun blue tape can be, and for contributing to the exfoliation work in Chapter 5. And I'd like to express my gratitude to Dr.\,David Leipold and Prof.\,Erich Runge from Ilmenau, who performed the FEM modelling for Chapter 7. Your ability to make sense of my stream of consciousness emails is astonishing, and your insights have been extremely valuable.

Thanks to my friends for their encouragement and distraction away from the lab. A special mention must go to Chlo{\"e} - from The Muppets to OWLS to to lambs' ears, we've had some truly excellent times. Thank you for showing me the joy of a nice cup of tea, and just how awkward turtles can be. 

Last but not least, thanks to my parents. For everything.
\end{acknowledgements}
